---
title: "EasternCanadaAAC Manual"
subtitle: "v.`r SpaDES.core::moduleMetadata(module = 'EasternCanadaAAC', path = '..')$version`"
date: "Last updated: `r Sys.Date()`"
output:
  bookdown::html_document2:
    toc: true
    toc_float: true
    theme: sandstone
    number_sections: false
    df_print: paged
    keep_md: yes
editor_options:
  chunk_output_type: console
bibliography: citations/references_EasternCanadaAAC.bib
link-citations: true
always_allow_html: true
---

# EasternCanadaAAC Module

(ref:EasternCanadaAAC) *EasternCanadaAAC*

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE
)

dir.create("figures", showWarnings = FALSE)
```

---

## Authors

```{r}
paste(as.character(SpaDES.core::moduleMetadata(
  module = "EasternCanadaAAC",
  path = ".."
)$authors), collapse = ", ")
```

---

## Module Overview

### Summary

The **EasternCanadaAAC** module calculates the Annual Allowable Cut (AAC) using a simplified Hanzlik method.

It:
- Uses yield tables and stand age distribution
- Computes optimal rotation age
- Estimates sustainable harvest volume
- Supports dynamic replanning

👉 *“This module translates forest structure into a sustainable harvest level.”*

---

## Module Inputs

```{r}
df_inputs <- SpaDES.core::moduleInputs("EasternCanadaAAC", path = "..")
knitr::kable(df_inputs,
             caption = "Module input objects.")
```

---

## Parameters

```{r}
df_params <- SpaDES.core::moduleParams("EasternCanadaAAC", path = "..")
knitr::kable(df_params,
             caption = "Module parameters.")
```

---

## Module Outputs

```{r}
df_outputs <- SpaDES.core::moduleOutputs("EasternCanadaAAC", path = "..")
knitr::kable(df_outputs,
             caption = "Module outputs.")
```

---

## Events

- **init**  
  - Computes Hanzlik parameters from yield tables  

- **plan**  
  - Calculates AAC  
  - Repeats every `replanInterval` years  

---

## Example Run (Standalone)

```{r}
library(SpaDES.core)

sim <- simInit(
  times   = list(start = 0, end = 1),
  modules = "EasternCanadaAAC",
  paths   = list(modulePath = ".."),
  options = list(
    spades.checkpoint = FALSE,
    spades.save       = FALSE,
    spades.progress   = FALSE
  )
)

sim <- spades(sim)

sim$AAC
```

---

## Notes

- If no input data are supplied:
  - The module generates internal test data  
- If yield files are available:
  - They are automatically used  
- If inputs are supplied externally:
  - They override internal generation  

---

## Links to Other Modules

This module is designed to integrate with:

- A classifier module providing `analysisUnitMap`
- Data preparation modules providing yield tables and stand age

---

## Getting Help

For issues or questions:
- Use the GitHub repository issues page

---

## References