---
title: "EasternCanadaAAC Manual"
subtitle: "v.`r SpaDES.core::moduleMetadata(module = 'EasternCanadaAAC', path = '..')$version`"
date: "Last updated: `r Sys.Date()`"
output:
  bookdown::html_document2:
    toc: true
    toc_float: true
    theme: sandstone
    number_sections: true
    df_print: paged
    keep_md: yes
editor_options:
  chunk_output_type: console
link-citations: true
always_allow_html: true
---

# EasternCanadaAAC Module

(ref:EasternCanadaAAC) *EasternCanadaAAC*

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE
)

dir.create("figures", showWarnings = FALSE)
```

---

## Authors

```{r}
paste(as.character(SpaDES.core::moduleMetadata(
  module = "EasternCanadaAAC",
  path = ".."
)$authors), collapse = ", ")
```

---

# 1. Overview

## Summary

The **EasternCanadaAAC** module calculates Annual Allowable Cut (AAC) using a simplified implementation of the Hanzlik method.

The module translates forest structure (age, yield, and area) into a sustainable harvest level.

---

## What the module does

* Computes rotation age from yield tables (based on MAI)
* Separates forest into:

  * Mature stands (harvestable)
  * Immature stands (growing)
* Integrates effective harvestable area
* Computes AAC per Analysis Unit (AU)
* Aggregates total AAC

---

## Key idea

AAC is calculated as:

**AAC = (Mature Volume / Rotation Period) + Growth**

Where:

* Mature volume comes from stands older than rotation age
* Growth comes from younger stands

---

# 2. Inputs

```{r}
df_inputs <- SpaDES.core::moduleInputs("EasternCanadaAAC", path = "..")
knitr::kable(df_inputs, caption = "Module input objects.")
```

### Description of inputs

* **analysisUnitMap** → assigns each pixel to an AU
* **standAgeMap** → stand age per pixel
* **pixelGroupMap** → unique pixel identifier
* **pixelAreaDT** → effective (harvestable) area per pixel
* **yieldTables** → yield curves per AU

---

# 3. Parameters

```{r}
df_params <- SpaDES.core::moduleParams("EasternCanadaAAC", path = "..")
knitr::kable(df_params, caption = "Module parameters.")
```

---

# 4. Outputs

```{r}
df_outputs <- SpaDES.core::moduleOutputs("EasternCanadaAAC", path = "..")
knitr::kable(df_outputs, caption = "Module outputs.")
```

---

## Key outputs

* **AAC** → total allowable cut (m³/year)
* **AAC_by_AU** → breakdown per analysis unit
* **hanzlikPars** → rotation age and growth parameters

---

# 5. Methodology

## Step 1: Yield processing

Each yield table is converted into:

* Volume (V)
* Increment (I)
* Rotation age (R)

Rotation age is defined as:

> Age at which Mean Annual Increment (MAI = V(t)/t) is maximized

---

## Step 2: Pixel-level data

Each pixel contributes:

* Analysis Unit (AU)
* Age
* Effective area

---

## Step 3: Separation of stands

* Mature stands: age ≥ R
* Immature stands: age < R

---

## Step 4: AAC calculation

For each AU:

* Mature volume is summed across pixels
* Growth is summed from immature stands

Then:

**AAC = (V_mature / Rotation Period) + I_total**

---

# 6. Example Run

```{r}
library(SpaDES.core)

sim <- simInit(
  times   = list(start = 0, end = 1),
  modules = "EasternCanadaAAC",
  paths   = list(modulePath = ".."),
  options = list(
    spades.checkpoint = FALSE,
    spades.save       = FALSE,
    spades.progress   = FALSE
  )
)

sim <- spades(sim)

sim$AAC
sim$AAC_by_AU
```

---

# 7. Notes

* If inputs are missing, synthetic data are generated
* Yield curves can be:

  * Real (.yld files)
  * Synthetic (for testing)
* Effective area integrates:

  * protected areas
  * riparian buffers
  * landbase constraints

---

# 8. Integration

This module is designed to work with:

* Classifier module (providing AU and area)
* Landbase module (constraints)
* Yield preparation module

---

# 9. Interpretation

* Higher AAC → more mature forest or higher growth
* Lower AAC → younger forest or constrained area

---

# 10. References
